Behavior Driven Development in Haskell

### 2012-05-23 paper.tex
more fix.

\noindent We can write this by copy-and-pasting from an interpreter.
It's worth explaining that we can specify operation sequences:

@@

\noindent But example annotations are useful for users but 
it is not used as test case from the developer point of view (before we implemented {\tt doctest}).

>>>>

\noindent The first line starts with {\tt >>>} and an expression follows. The second line contains its result. We can write this by copy-and-pasting from an interpreter and modifying the prompt.
It's worth explaining that we can specify operation sequences:

@@

\noindent Example annotations are useful for users but 
it is not used as test case from the developer point of view (before we implemented {\tt doctest}).
